Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-09-21 tex/main/manuscript.tex
摘要更新

%tag 摘要
\begin{abstract}
	In the context of regime shifts, understanding the complex relationship between human societies and water resources utilization provides underlying supports to development in a coordinated way at a basin scale. However, there is still lacking of effective method to detect regime shifts of water utilization, with much fewer attempts to develop theoretical models to explain their transition phases as well. Here, by integrating three different dimensions of water utilization (stress, tendentiousness and pattern), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to detect regime shifts. By applying this index to the Yellow River Basin, China, we summarized a general transition framework of regimes, which gives a sketch of relationships between human societies and their water utilization. Based on the framework, transition phases within the three regimes and accompanying development traps can be well understood, as a useful guideline for the Yellow River to develop in a coordinated way.
\end{abstract}

>>>>

%tag 摘要
\begin{abstract}
	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
	However, there is still lacking of effective method to detect regime shifts of water utilization linking to social changes, with much fewer attempts to develop theoretical models to explain their transition phases as well. 
	Here, by integrating three different dimensions of water utilization (stress, tendentiousness and pattern), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to detect regime shifts. 
	By applying this index to the Yellow River Basin, China, we summarized a general transition framework of regimes, which gives a sketch of relationships between human societies and their water utilization. 
	Based on the framework, transition phases within the three regimes and accompanying development traps can be well understood, as a useful guideline for the Yellow River to develop in a coordinated way.
\end{abstract}
